\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provides euro and other symbols
\else % if luatex or xelatex
  \usepackage{unicode-math}
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\usepackage{hyperref}
\hypersetup{
            pdftitle={Publications},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother


\title{Publications}
\date{}

\begin{document}
\maketitle

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-karlsson_teleost_2019}{}%
Karlsson, Cecilia, Jay Willis, Matishalin Patel, and Theresa Burt de
Perera. 2019. ``Teleost Fish Can Accurately Estimate Distance
Travelled.'' \emph{bioRxiv}, 834341.
\url{https://doi.org/10.1101/834341}.

\leavevmode\hypertarget{ref-patel_crystal_2019-1}{}%
Patel, Matishalin, Ben Raymond, Michael B. Bonsall, and Stuart A. West.
2019. ``Crystal Toxins and the Volunteer's Dilemma in Bacteria.''
\emph{J. Evol. Biol.} 32 (4): 310--19.
\url{https://doi.org/10.1111/jeb.13415}.

\leavevmode\hypertarget{ref-patel_can_2019}{}%
Patel, Matishalin, Stuart A. West, and Jay M. Biernaskie. 2019. ``Can
Natural Selection Favour Indiscriminate Spite?'' \emph{bioRxiv}, 745638.
\url{https://doi.org/10.1101/745638}.

\leavevmode\hypertarget{ref-vila_uncovering_2019}{}%
Vila, Jean C. C., Matt L. Jones, Matishalin Patel, Tom Bell, and James
Rosindell. 2019. ``Uncovering the Rules of Microbial Community
Invasions.'' \emph{Nat Ecol Evol} 3 (8): 1162--71.
\url{https://doi.org/10.1038/s41559-019-0952-9}.

\end{document}
